Nix for Polyglot, Reproducible Data Science Workflows

### 2025-11-04 paper.qmd
chore: rephrase Nix and container technologies

Provisioning [Nix]{.pkg} in container images lowers the burden to install it on
the operating system of the host.

>>>>

By combining the strengths of Nix and container technologies, it is possible to
enhance both build-time and runtime isolation. For example, installing [Nix].pkg
directly into container images reduces the setup overhead by avoiding the need
to install derivations into the host operating system's `/nix` directory.
